----------------------------------------
Welcome....
----------------------------------------

Utility Manager
----------------------------------------------------------------------------
This application includes a Task Manager for linux similar to the Ms Windows
and a Troubleshooter to safely remove a Drive when its busy in some process.
----------------------------------------------------------------------------

Steps to run the application:-
------------------------------


1)Run the utilitymanager.exe file.

a)TASKMANAGER:-
  -------------

1)Click on the Taskmanager button.
2)It will open the taskmanager GUI.
3)Click  on system Info  to get the Basic Info, Memory Info and Battery Info and details.
4)Click on the Network Info tab to know about the sent and received data.
5)Click on the processes tab to view current running processes and their details.

b)TROUBLESHOOTER:-
  ----------------

1)Click on the Troubleshoot Disks button.
2)If no device is mounted, it will show an error message.
3)If the devices are mounted,it will show the list of the mounted devices.
4)Select the device to unmount and click on the safely remove button.
5)If the device is not selected then it will give an error message.
6)If no process is running then it will show no process running and
  click on unmount to unmount the device.It will unmount the device.
7)If a/many process/es are running it will show there PID.
8)If you click on the unmount it will kill the process and unmount the Drive.

Files Description:-
-------------------
This application has three windows in GUI namely:-
1)Taskmanger
2)SafelyRemove
3)Unmount Disk
Corresponding to each part, There is a .h and .ui file for there header files and GUI.

All the three windows are assembled in utility manager which has its own .h and .ui file and also has a .cpp file which performs all the tasks.

main.cpp	       	 To call the main window of the application.
main.o	        	 To 
Makefile
moc_utilitymanager.cpp
moc_utilitymanager.o
safe_remove.ui  	 To provide GUI for the safely remove option.
string_Memory.h 	 Header file to simplify repeated use of string functions
taskManager.ui  	 To provide GUI for the Taskmanager window.
ui_safe_remove.h 	 This file is automatically generated when we build the program by the QT4 application.
ui_taskManager.h	 This file is automatically generated when we build the program by the QT4 application.
ui_unmountdisk.h	 This file is automatically generated when we build the program by the QT4 application.
ui_utilitymanager.h	 This file is automatically generated when we build the program by the QT4 application.
unmountdisk.ui		 To provide GUI for the Unmount Disk function.
utility_Manager		 The main executable file in which the whole application runs.
utilitymanager.cpp	 This file contains the c++ codes of the whole project.
utilitymanager.h	 This contains all the header files of the whole project.	
utilitymanager.o
utilitymanager.ui	 To provide GUI for the Main Window which shows two Push Buttons.
